### 2020-10-27 README.Rmd
working on small example

set.seed(76)
ex_cv_grid <- spatialBlock(
  speciesData = ex_growth_df, theRange = 5, verbose = FALSE, k = 2
)

@@

bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = cv_fold_size, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

bw_cv_grid_sf <- bw_cv_grid$blocks %>%
  st_as_sf()

>>>>

set.seed(76)
#ex_cv_grid <- spatialBlock(
#  speciesData = ex_growth_df, theRange = 5, verbose = FALSE, k = 2
#)

# Add foldID to data
ex_growth_df <- ex_growth_df %>% 
  mutate(
    foldID = ex_cv_grid$foldID
  )

# Visualize grid. Why does fold 19 repeat?
ex_cv_grid$plots +
  geom_sf(data = ex_growth_df, aes(col=factor(foldID)), size = 1)

ex_cv_grid <- ex_cv_grid$blocks %>%
  st_as_sf()

@@
